\documentclass{article}
\usepackage{fancyhdr}
\input{../../preamble}

\title{Group}
\author{Hyoung Joon, Kim}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

\newpage

\section{Group}
\subsection{Introduction and Basic Definitions}
A group is a fundamental algebraic structure consisting of a set equipped with a binary operation that satisfies certain axioms. Groups are widely used in various fields of mathematics, including algebra, geometry, and number theory, as well as in physics and computer science.


Now, we provide the formal definition of a group.
% Definition of Group
\begin{defn}{Group}{GP}
A \emph{group} is a set \( G \) equipped with a binary operation
\(\cdot : G \times G \to G\) satisfying the following axioms:
\begin{enumerate}[label=(\roman*)]
    \item (\emph{Closure}) For all \( a, b \in G \), the result of the operation \( a \cdot b \) is also in \( G \).
    \item (\emph{Associativity}) For all \( a, b, c \in G \), \( (a \cdot b) \cdot c = a \cdot (b \cdot c) \).
    \item (\emph{Identity Element}) There exists an element \( e \in G \) such that for every element \( a \in G \), \( e \cdot a = a \cdot e = a \).
    \item (\emph{Inverse Element}) For each \( a \in G \), there exists an element \( b \in G \) such that \( a \cdot b = b \cdot a = e \), where \( e \) is the identity element.
\end{enumerate}
Furthermore, if the binary operation is commutative, i.e., \(a \cdot b = b \cdot a\) for all \(a, b \in G\), then the group is called an \emph{abelian group}.
\end{defn}

Here, we can weaken the conditions (iii) and (iv) of the \hyperref[defn:GP]{Definition~\ref{defn:GP}} as follows:
% Remark on Weakened Group Definition
\begin{rem}{}{GPWeaken}
Change condition (iii) and (iv) of \hyperref[defn:GP]{Definition~\ref{defn:GP}} to the following:
\begin{enumerate}[label=(\roman*)]
    \item[(iii)$'$] (\emph{Left Identity Element}) There exists an element \( e \in G \) such that for every element \( a \in G \), \( e \cdot a = a \).
    \item[(iv)$'$] (\emph{Left Inverse Element}) For each \( a \in G \), there exists an element \( b \in G \) such that \( b \cdot a = e \), where \( e \) is the identity element.
\end{enumerate}
Then, the set \( G \) with the binary operation \(\cdot\) still forms a group.
\end{rem}

\begin{proof}
It is left as an exercise.
\end{proof}

\begin{defn}{Subgroup}{SubGP}
    Let $(G,\ \cdot)$ be a group. A subset $H \in G$ is called a \emph{subgroup} of $G$ if $H$ satisfies the following conditions:
    \begin{enumerate}[label=(\roman*)]
        \item (\emph{Closure}) For all \( a, b \in H \), \( a \cdot b \in H \).
        \item (\emph{Identity Element}) The identity element \( e \in G \) is in \( H \).
        \item (\emph{Inverse Element}) For each \( a \in H \), \(a^{-1} \in H\).
    \end{enumerate} 
\end{defn}

\end{document}